r5r: Rapid Realistic Routing with R5 in R

### 2020-09-18 r-package/paper2020/paper2020.Rmd
updates detailed_itineraries paper section

### Detailed itineraries

Allows one to get the fastest or multiple alternative routes between a set of
origins and destinations.

Create simple example here and plot the result below

@@

>>>>

### Calculate detailed itineraries

Often enough one wants more information on the itineraries between 
origin/destination pairs than simply the travel time. For such cases, the 
package includes the `detailed_itineraries()` function, which also takes travel 
restrictions as inputs, but outputs a much more detailed data set at the trip 
segment level. Another key feature of this function is that it (optionally) 
provides multiple alternative routes between origin/destination pairs:

```{r, message = FALSE}
# load points of interests and set origin and destination
points <- read.csv(file.path(data_path, "poa_points_of_interest.csv"))
origins <- points[c(10, 14),]
destinations <- points[c(12, 15),]

# set restrictions
mode <- c("WALK", "TRANSIT")
max_walk_dist <- Inf
max_trip_duration <- 120
departure_datetime <- as.POSIXct("13-03-2019 14:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")

dit <- detailed_itineraries(r5r_core,
                            origins,
                            destinations,
                            mode,
                            departure_datetime,
                            max_walk_dist,
                            shortest_path = FALSE)

dit
```

Since the `shortest_path` argument has been set to `FALSE`, `dit` holds 
information for multiple itineraries between the same origin/destination pairs:

```{r, message = FALSE}
setDT(copy(dit))[, .(n_itineraries = uniqueN(option)), by = .(fromId, toId)]
```

Had `shortest_path` been set to `TRUE`, only the shortest path would have been 
returned:

```{r, message = FALSE}
dit_short <- detailed_itineraries(r5r_core,
                                  origins,
                                  destinations,
                                  mode,
                                  departure_datetime,
                                  max_walk_dist,
                                  shortest_path = TRUE)

setDT(copy(dit_short))[, .(n_itineraries = uniqueN(option)), by = .(fromId, toId)]
```

@@

`detailed_itineraries()` output is a `sf` object, which means that each trip segment is associated to a geometry
